### 2021-10-17 docs/manuscript/manuscript.tex
Improve Fig 1
Improve description of isomorph identification

\begin{figure}[!h]
%  \centering
%  \includegraphics[width=\textwidth]{figures/metodos/Fig1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Heatmap of spatiotemporal expression profile of a GRN where blue
    colors represent lower expression and red colors represent higher
    expression.
 \label{fig:model}
\end{figure}

@@

In order to group all the isomorphic (i.e. topologically equivalent) networks from
the totality (2061) of sampled GRNs we used a
classification algorithm that selected a random GRN and generated all
isomorphs of that GRN by interchanging rows of the adjacency matrix
($i \leftrightarrow j$) while interchanging the corresponding columns
($i+1 \leftrightarrow j+1$). The
algorithm then compared all six isomorphs with other GRN and classified the
topologies in the same group if they were isomorphic networks.

>>>>

\begin{figure}[!h]
%  \centering
%  \includegraphics[width=\textwidth]{figures/metodos/Fig1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Heatmap of spatiotemporal expression profile of a GRN where blue
    colors represent lower expression and red colors represent higher
    expression. Time axis goes from 0 to 500 integration steps. Horizontal
    axis represents the morphogenetic field, i. e. cells from 1 to 30 for
    each gene.
 \label{fig:model}
\end{figure}

@@

In order to group all the isomorphic (i.e. topologically equivalent) networks from
the totality (2061) of sampled GRNs we used a
classification algorithm that selected a GRN and generated all
isomorphs of that GRN by interchanging rows of the adjacency matrix
($i \leftrightarrow j$) while interchanging the corresponding columns
($i+1 \leftrightarrow j+1$). This kind of transformation of the adjacency
matrix results in isospectral graphs that are also isomorphic to the
original graph and is comparable to generate a permutation matrix $P$ and
multiplying $PMP^{T}$, where $M$ is the adjacency matrix and $P^{T}$ the
transpose of $P$. The algorithm then compared these isomorphs with another
GRN and classified the topologies in the same group if at least one of the
transformed adjacency matrices (or the original one) was identical to that
of the other GRN, i. e., if they were isomorphic networks.
